\section{Discussion}
\label{s_discuss}
The use of historical data to develop a forward model has several limitations. The biggest limitation is in the size of this data set, both in terms of the number of countries and in the range of years that it includes.  This model is intrinsically limited by the small sample size and the degree to which the global landscape changes over time. With only 10 states that have acquired nuclear weapons throughout history, there is large uncertainty in any quantatitative analysis. While the analysis has identified factors that are correlated to weapons programs, there is insufficient data to confirm causal relationships.

Since the data set already includes all countries that have pursued nuclear weapons, the missing countries would only be relevant if they had pursuit scores of 4 or larger, thus reducing the time-integrated likelihood of pursuit associated with such scores. Due to the influence of nuclear technology, a non-nuclear state could theoretically have a maximum pursuit score of 7. Considering that the majority of states that have high potential military spending and major historical conflicts have already been incorporated, this further reduces the potential maximum score to below 5, even if all other factors are maximized.  A large fraction of states in the world are expected to have scores on the order of 1-3, and thus not alter the distribution shown in \ref{fig:likely}.

A more important addition to the database would be data for each country for all years between 1940 (before the first historical pursuit) and the year of pursuit and/or aquisition.  This would allow the direct calculation of an annual probability of pursuit as a function of the pursuit score.  The current model for converting a time-integrated likelihood to an annual probability inherently assumes that the pursuit score for the countries in the data set is constant for all the years prior to the decision to pursue nuclear weapons.  An effort fo assemble this data would be a valuable contribution to this modeling effort.



