%\documentclass{proc}  % 2-column format
\documentclass[12pt]{paper}
%\documentclass{ntmanuscript}
%\documentclass[review]{elsarticle}
\usepackage{mathptmx} % Nearly Times New Roman
\usepackage[acronym,toc]{glossaries}
\include{acros}
%\makeglossaries
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{listings}
\usepackage{textcomp}
%\usepackage{ulem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in



\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}
\definecolor{burntorange}{rgb}{0.8, 0.33, 0.0}
\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}

\lstset{
    %backgroundcolor=\color{lbcolor},
    language={C++},
    tabsize=4,
    rulecolor=\color{black},
    upquote=true,
    aboveskip={1.5\baselineskip},
    belowskip={1.5\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    basicstyle=\scriptsize\ttfamily\color{green!40!black},
    keywordstyle=\color[rgb]{0,0,1.0},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{0.627,0.126,0.941},
    numberstyle=\color[rgb]{0,1,0},
    identifierstyle=\color{black},
    captionpos=t,
}

\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}
\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\Cyclus}{\cyclus}
\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%

\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%\begin{frontmatter}
\title{State-Level Decision-Making In Cyclus to Assess Multilateral Enrichment}

% Authors. Separated by commas
\input{authors}
\date{}
% Institutes of the authors
\input{institutions}
% Information concerning the person submitting the manuscript
%\submitter{Meghan B. McGarry}
%\submitteraddress{1500 Engineering Drive, Madison, WI, USA}
%\submitteremail{mbmcgarry@wisc.edu}

% No more than three keywords, though each can be a phrase
%\keywords{fuel cycle, simulatiom, non-proliferation}
\maketitle

% I. Motivation
% x   -  Identify Factors that motivate
% x  II. Benchmark model against historical data:
% x A. Develop historical database
% x   - What sources?
% x   - What model to convert to 10pt scale?
% x        - Conflict
% x B. Determine relative weighting of factors
% x   - Calculate values for historical database
% x   - PCA to determine relative weights
% ** C. Table of State Score Results
% III. Develop forward model 
%   - From score to a likelihood, using historical data
% IV. Limitations of model
%   - small dataset
%   - threshold value for proliferation
%   - no good model for scientific network
% V. Future work
%   - Apply to case study (JCPOA?)
% VI Appendix of factor conversions

\begin{abstract}

 Proposed treaties and agreements that aim to reduce the spread of nuclear weapons are often stalled by skepticism regarding their efficacy. For example, the concept of multilateral enrichment, in which multiple states co-own and operate an enrichment facility, has the potential to reduce the spread of enrichment technology. However, detractors point to the improved international networking opportunities inherent in multinational organizations as a risk factor for increased proliferation. A framework to compare the relative risk between a multilateral enrichment paradigm and the status quo, on a regional scale, can help inform the discussion and potentially identify ways to reduce global risk of nuclear proliferation. As part of the Consortium for Verification Technology, the Cyclus fuel cycle simulator is being used as a test-bed for the development of such new technologies and approaches to treaty verification. Cyclus is a systems-level nuclear fuel cycle simulator that models the interactions between actors in the nuclear arena. While designed to track the flow of nuclear material between facilities, Cyclus also incorporates an innovative Facility-Institution-Region hierarchy that can capture the dynamics of state-level interactions. Drawing on social science literature to identify factors that motivate states to pursue weapons programs, we have developed a regional proliferation model that captures causes and effects of state-level nuclear weapons proliferation. The model identifies eight key factors that influence a state’s decision to pursue nuclear weapons. These factors include motivations internal to the state, such as military spending and governing structure, as well as interactive factors such as conflict between states. Historical data is used to identify the relative importance of these factors and translate them into a likelihood of pursuing a weapon. The model also provides a feedback mechanism such that acquisition of a nuclear weapon by one state influences the decision-making of the other states. This model will be used to assess the effectiveness of policy approaches, such as multilateralization of the fuel cycle, that seek to reduce the regional risk of proliferation over time.

\end{abstract}


%\end{frontmatter}


\input{introduction}
\input{factors}
\input{methods}
\input{discussion}
\input{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{small}
\bibliographystyle{ANSurl}
\bibliography{../zotero_160516,../zotero_adds_160603,../manual_fixes,../websites_manual}
\end{small}
\end{document}
