%\documentclass{proc}  % 2-column format
\documentclass[12pt]{paper}
%\documentclass{ntmanuscript}
%\documentclass[review]{elsarticle}
\usepackage[acronym,toc]{glossaries}
\include{acros}
%\makeglossaries
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{ulem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in


\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
    %backgroundcolor=\color{lbcolor},
    language={C++},
    tabsize=4,
    rulecolor=\color{black},
    upquote=true,
    aboveskip={1.5\baselineskip},
    belowskip={1.5\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    basicstyle=\scriptsize\ttfamily\color{green!40!black},
    keywordstyle=\color[rgb]{0,0,1.0},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{0.627,0.126,0.941},
    numberstyle=\color[rgb]{0,1,0},
    identifierstyle=\color{black},
    captionpos=t,
}

\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}
\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\Cyclus}{\cyclus}
\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%

\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%\begin{frontmatter}
\title{Modeling Material Diversion with the Cyclus Nuclear Fuel Cycle Simulator
}

% Authors. Separated by commas
\input{authors}
\date{}
% Institutes of the authors
%\input{institutions}
% Information concerning the person submitting the manuscript
%\submitter{Meghan B. McGarry}
%\submitteraddress{1500 Engineering Drive, Madison, WI, USA}
%\submitteremail{mbmcgarry@wisc.edu}

% No more than three keywords, though each can be a phrase
%\keywords{fuel cycle, simulatiom, non-proliferation}
\maketitle



\begin{abstract}

  Already the dominant source of clean energy, nuclear power is growing at a
  rapid pace.  While beneficial to a world confronting climate change, the
  nuclear security and non-proliferation impacts of expanding nuclear power
  are increasingly consequential.  As a result, it is imperative to develop
  credible methods to verify compliance with treaties that control fissile
  material production, such as the \gls{NPT} or a potential
  \gls{FMCT}. As part of the Consortium for Verification
  Technology, the Cyclus fuel cycle simulator is being used to model current
  and next-generation nuclear fuel cycles and inform treaty verification.  Cyclus
  is an agent-based, systems-level simulator that tracks discrete material flow
  through the entire fuel cycle, from mining through burnup in reactors to a
  repository, or alternatively through one or more iterations of reprocessing.
  Cyclus includes social-behavior models of individual actors, facilitating the
  study of clandestine material diversion from declared fuel cycles.  Cyclus
  also features a region-institution-facility hierarchy that can incorporate the
  effects of tariffs and sanctions in a regional or global context.  This paper
  presents initial Cyclus simulations of highly enriched uranium diversion from
  a declared once-through fuel cycle.  Material flow signals are analyzed using
  anomaly detection techniques to identify diversion.

\end{abstract}


%\end{frontmatter}


\input{introduction}
\input{methods}
\input{results}
\input{discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ANSurl}
\bibliography{../zotero_150923,../websites_manual}
%\bibliography{/Users/mbmcgarry/git/papers/zotero_150918}
\end{document}
