%\documentclass{proc}  % 2-column format
\documentclass[12pt]{paper}
%\documentclass{ntmanuscript}
%\documentclass[review]{elsarticle}
\usepackage{mathptmx} % Nearly Times New Roman
\usepackage[acronym,toc]{glossaries}
\include{acros}
%\makeglossaries
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{listings}
\usepackage{textcomp}
%\usepackage{ulem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in



\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
    %backgroundcolor=\color{lbcolor},
    language={C++},
    tabsize=4,
    rulecolor=\color{black},
    upquote=true,
    aboveskip={1.5\baselineskip},
    belowskip={1.5\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    basicstyle=\scriptsize\ttfamily\color{green!40!black},
    keywordstyle=\color[rgb]{0,0,1.0},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{0.627,0.126,0.941},
    numberstyle=\color[rgb]{0,1,0},
    identifierstyle=\color{black},
    captionpos=t,
}

\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}
\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\Cyclus}{\cyclus}
\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%

\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%\begin{frontmatter}
\title{Cyclus As a Synthetic Testbed of Systems-Level Diversion Signatures}

% Authors. Separated by commas
\input{authors}
\date{}
% Institutes of the authors
\input{institutions}
% Information concerning the person submitting the manuscript
%\submitter{Meghan B. McGarry}
%\submitteraddress{1500 Engineering Drive, Madison, WI, USA}
%\submitteremail{mbmcgarry@wisc.edu}

% No more than three keywords, though each can be a phrase
%\keywords{fuel cycle, simulatiom, non-proliferation}
\maketitle



\begin{abstract}

  Already the dominant source of clean energy, nuclear power is growing at a
  rapid pace.  While beneficial to a world confronting climate change, the
  nuclear security and non-proliferation impacts of expanding nuclear power
  will become more consequential.  As a result, it is imperative to develop
  credible methods to verify compliance with treaties that control fissile
  material production, such as the Non-Proliferation Treaty or a potential
  Fissile Material Cutoff Treaty. As part of the Consortium for Verification
  Technology, the Cyclus fuel cycle simulator is being used as a testbed for the
  development of new technologies and analysis approaches to treaty
  verification. Cyclus is an agent-based, systems-level simulator that tracks
  discrete material flow through the entire fuel cycle, from mining through
  burnup in reactors to a repository, or alternatively through one or more
  iterations of reprocessing. A systems-level view facilitates the study of
  correlated signals from different facilities that combine to form identifiable
  signatures of clandestine activity. Cyclus also includes a
  region/institution/facility hierarchy that can incorporate the effects of
  tariffs and sanctions in regional or global contexts.  Cyclus enables social-
  behavioral modeling of the interactions between individual facilities or
  regions.  This paper presents the first use of Cyclus to simulate nuclear
  material diversion from the fuel cycle using a variety of contemporaneous signals:
  material flow, facility power consumption, effluent emissions (including
  geospatial distribution), event-logs.  Multiple signal modalities can be
  analyzed in concert using anomaly detection techniques to identify signatures
  of material diversion or other signatures of clandestine nuclear weapons
  development.  The Cyclus testbed can then be used to examine treaty
  verification techniques and inspection regimens to to inform their sensitivity
  and limitations.

\end{abstract}


%\end{frontmatter}


\input{introduction}
\input{methods}
\input{signatures}
\input{results}
\input{discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{small}
\bibliographystyle{ANSurl}
\bibliography{../zotero_160516,../zotero_adds_160603,../manual_fixes,../websites_manual}
\end{small}
\end{document}
